Untitled

### 2025-03-20 script/r/draft.Rmd
country heterogeneity

>>>>

```{r}
library(readxl)
library(tidyr)

countries <- data_final %>% pull(iso) %>% unique()

wb_gov <- read_excel("data/data_raw/wb_gov/wgidataset.xlsx")

wb_gov %<>%
  select(code, year, indicator, estimate) %>%
  mutate(estimate = na_if(estimate, ".."))

wb_gov %<>%
  pivot_wider(names_from = indicator, values_from = estimate)

wb_gov %<>%
  rename(
    ctrl_corr = cc,
    voice_acc = va,
    pol_stab = pv,
    gov_eff = ge,
    reg_qty = rq,
    rol = rl,
    iso = code
  ) %>%
  mutate(across(c(
    ctrl_corr, voice_acc, pol_stab, gov_eff, reg_qty, rol
  ), as.numeric))

wb_gov %<>%
  mutate(round = case_when(
    between(year, 2011, 2013) ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

wb_gov %<>%
  group_by(iso, round) %>%
  filter(!is.na(round)) %>%
  mutate(
    ctrl_corr_mean = ifelse(all(is.na(ctrl_corr)), NA_integer_, mean(ctrl_corr, na.rm = TRUE)),
    voice_acc_mean = ifelse(all(is.na(voice_acc)), NA_integer_, mean(voice_acc, na.rm = TRUE)),
    pol_stab_mean = ifelse(all(is.na(pol_stab)), NA_integer_, mean(pol_stab, na.rm = TRUE)),
    gov_eff_mean = ifelse(all(is.na(gov_eff)), NA_integer_, mean(gov_eff, na.rm = TRUE)),
    reg_qty_mean = ifelse(all(is.na(reg_qty)), NA_integer_, mean(reg_qty, na.rm = TRUE)),
    rol_mean = ifelse(all(is.na(rol)), NA_integer_, mean(rol, na.rm = TRUE)),
  ) %>%
  ungroup()

wb_gov%<>%
  mutate(gov_cap = rowMeans(select(., gov_eff_mean, reg_qty_mean), na.rm = TRUE))

wb_gov %<>%
  select(
    iso,
    round,
    ctrl_corr_mean,
    voice_acc_mean,
    pol_stab_mean,
    gov_eff_mean,
    reg_qty_mean,
    rol_mean,
    gov_cap
  ) %>%
  distinct(iso, round, .keep_all = TRUE)

wb_gov %<>%
  filter(iso %in% countries)

data_final %<>% left_join(wb_gov, by = c("iso", "round"))

saveRDS(data_final, file = "data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")

```{r}
# Load dplyr package
library(dplyr)

# Assuming your data is in data_final and has columns ctrl_corr_mean and spl
percentile_below_neg_0_5 <- data_final %>%
  filter(spl == 1) %>%  # Filter for spl == 1
  summarise(
    total_count = n(),  # Total number of observations where spl == 1
    below_neg_0_5_count = sum(ctrl_corr_mean < -0.5)  # Count values less than -0.5
  ) %>%
  mutate(
    percentile = (below_neg_0_5_count / total_count) * 100  # Calculate the percentage
  )

# Display the result
print(percentile_below_neg_0_5)
